\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Manish Kumar}
\address{+91 7834898501 \\ Delhi, India} 
\address{\href{mailto:manishdotkr@gmail.com}{manishdotkr@gmail.com} \\ \href{https://www.linkedin.com/in/manishdotkr}{linkedin} \\ \href{https://manish.kr}{Portfolio}}  %


\begin{document}
%----------------------------------------------------------------------------------------
% SKILLS
%----------------------------------------------------------------------------------------
\vspace{-1.25em} % used to remove spaces
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
CI/CD & Jenkins , github action , Github Workflows \\
Deployments & Docker , Kubernetes , Helm , Containerization, AWS EC2 \\
IaC & Terraform , Cloudformation  \\
DevOps & Bash , Python , scripting , automation , Linux , Integration , Serverless  \\
Cloud(AWS) &  IAM, Fargate, VPC, S3, EC2, Lambda, Cloudfront, ALB, NLB, Route53\\
Dara Warehouse(AWS) &  Aurora(MySql), Redshift Cluster, zero-ETL Integration   \\
Security-Secrets Management & HashiCorp Vault, AWS Secrets Manager, Parameter Store, SSM Documents\\
\end{tabular}\\

\end{rSection}


%----------------------------------------------------------------------------------------
% EXPERIENCE
%----------------------------------------------------------------------------------------
% \vspace{-1.25em} % used to remove spaces
\begin{rSection}{EXPERIENCE}

\textbf{DevOps Engineer} \hfill July 2025 - Present\\
Wiom \hfill \textit{Gurugram , Haryana}
 \begin{itemize}
    \itemsep -3pt {} 
    \item Designed and set up EKS clusters across all environments, enabling seamless migration of workloads from ECS to EKS for improved scalability, stability, and control.
    \item Led deployment of high-scale production workloads (serving 1M+ active devices) on EKS, including PDO and core device communication services.
    \item Migrated critical services from ECS to EKS, ensuring high availability and reliability for device connectivity and functionality.
    \item Implemented canary deployments and session stickiness in both NLB and ALB for zero-downtime rollouts and consistent traffic routing.
    \item Deployed enterprise-grade MQTT broker (EMQX) on EKS with secure authentication, enabling command and instruction delivery to 1M+ connected devices.
    \item Provisioned and configured Redis clusters in production to support low-latency, high-throughput workloads.
    \item Automated error log monitoring and alerting for critical services, integrating with email notifications for proactive issue resolution.
    \item Coordinated with AWS teams on Timestream POC, preparing infrastructure documentation and reports to secure AWS credits.
    
    \item Deployed and managed AI-driven platforms on EKS, including:
        \begin{itemize}
            \item Call Analysis/QMS System – recording, transcribing, and analyzing support calls with AI-driven customer satisfaction scoring.
            \item AI Call-Agent Services – powering intelligent automation for customer interactions.
        \end{itemize}
    \item Implemented Uptime Kuma on EKS with persistent storage for real-time service health monitoring and uptime visibility.
 \end{itemize}

\textbf{Engineer: DevOps and Cloud Technologies} \hfill Oct 2022 - July 2025\\
Impressico Business Solutions \hfill \textit{Noida , UP}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Increased deployment efficiency by 40\% by managing Java backend on AWS ECS, orchestrating frontend hosting on S3 bucket, and implementing CI/CD pipelines using Jenkins for streamlined development workflows.
     \item Improved data processing capabilities by 53\% through orchestrating Redshift clusters deployment and seamlessly integrating them with existing Aurora clusters to empower AI/ML and data engineering capabilities
     \item Reduced system downtime through supervising project management and deployment across all environments to improve system functionality continuously
     \item Enhanced operational efficiency through collaboration with Devs for implementation of automation tools like pagehealth, awsOnOff and v2sanity python service
     \item Optimized infrastructure costs by 68.75\% by replacing NAT Gateway with NAT instance using amazon linux 3
     \item Improved compliance monitoring efficiency by 35\% through exclusive management of the ChatOps project, an in-house initiative designed to oversee all project repositories on GitHub and ensure compliance with company's rules and regulations.
 \end{itemize}

\end{rSection} 
%----------------------------------------------------------------------------------------
%	DEVOPS PROJECT
%----------------------------------------------------------------------------------------
\begin{rSection}{DEVOPS PROJECTS}
\vspace{-1.25em}
% ------------------------------------------------
\item \textbf{Manishboard} { Manishboard is a cloud-native dashboard built with Spring Boot and Kubernetes for seamless deployment and scalability. It leverages GitHub Actions for CI/CD automation and Helm for efficient management. Configured domain routing with SSL certificates through Kubernetes Ingress for secure API access. \href{https://github.com/manishboard}{(Github Repo)}}
% ------------------------------------------------
\item \textbf{Book Vault} { Developed Book Vault, a full-stack book management system using React and Node.js, implementing GitOps practices with GitHub Actions for CI/CD. Architected cloud infrastructure using Terraform to provision AWS resources, deployed containerized backend on Kubernetes running in EC2, and hosted frontend on GitHub Pages. Configured domain routing with SSL certificates through Kubernetes Ingress for secure API access. \href{https://github.com/book-vault}{(Github Repo)} \href{https://bookvault.manish.kr}{(Live)}}
% ------------------------------------------------
\item \textbf{Github Actions} { This repository contains a collection of GitHub Actions workflows designed to monitor the repository and pull requests, performing various operations based on predefined conditions. \href{https://github.com/manishdotkr/github-actions}{(Github Repo)}}
\end{rSection} 
%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Technology in Information Technology}, MSIT [IP University] \hfill {2022}\\
Percentage: 86.7.

{\bf Diploma in Mechanical Engineering}, PIT University \hfill {2017}\\

\end{rSection}

\end{document}
